Uncovering underlying high-level musical content in the time domain \\ \small Leveraging self-supervised neural networks, inductive bias, and aural skills to learn deep audio embeddings with applications to boundary detection tasks

### 2023-08-13 discussion/discussion.tex
Updates from Overleaf

While our results may not yet rival state-of-the-art benchmarks, they affirm we're on the right path and reveal the potential of this research direction. Importantly, we've seen that progress doesn't have to be expensive—though time and potential data copyright issues are considerations.

>>>>

The proposed embeddiograms are a promising new approach for music boundary detection. While they do not yet rival state-of-the-art methods, they are competitive with traditional handcrafted signal processing methods and can be trained on unlabeled audio files. This makes them a cost-effective and scalable solution for music boundary detection tasks.

### 2023-08-13 evaluation/evaluation.tex
Updates from Overleaf

\subsection{GTZAN dataset}
The GTZAN Genre Collection is a widely-used dataset for music genre classification tasks. It comprises 1,000 audio tracks that are each 30 seconds long. These tracks are evenly distributed across ten genres: blues, classical, country, disco, hip hop, jazz, metal, pop, reggae, and rock, each containing precisely 100 songs. The audio files are stored as WAV files with a sample rate of 22050 Hz \cite{GTZAN}.

\subsection{Million Song Dataset}
The Million Song Dataset (MSD) is a publicly available audio and metadata collection for a million contemporary popular music tracks.

@@

\subsection{SALAMI dataset}

@@

Note: We used SALAMI's original release from 2011, featuring 1,359 tracks.

>>>>

\subsection{The GTZAN dataset}
The GTZAN Genre Collection is a widely-used dataset for music genre classification tasks. It comprises 1,000 audio tracks that are each 30 seconds long. These tracks are evenly distributed across ten genres: blues, classical, country, disco, hip hop, jazz, metal, pop, reggae, and rock, each containing precisely 100 songs. The audio files are stored as WAV files with a sample rate of 22050 Hz \cite{GTZAN}.

\subsection{The Million Song Dataset}
The Million Song Dataset (MSD) is a publicly available audio and metadata collection for a million contemporary popular music tracks.

@@

\subsection{The SALAMI dataset}

@@

Note: We used SALAMI's original release, 2011, featuring 1,359 tracks.

### 2023-08-13 methods/subsections/implementation.tex
Updates from Overleaf

Our approach falls broadly under cognitive modeling, which seeks to simulate human cognitive processes and problem-solving through a computerized model. We advocate for exposure-based learning in music, encouraging active engagement with as many musical styles, genres, techniques, and learning methods as possible. This approach promotes comprehensive musical proficiency and efficient performance when encountering novel and unseen data in practical applications.

@@

Our implementation slightly modifies the \textit{contrastive learning of musical representations} (CLMR) method \cite{CLMR2021}, which learns valuable, discriminative music representations without explicit labels by contrasting positive augmentations of a musical piece against negative ones. CLMR falls under a branch of ML known as self-supervised learning (SSL) \cite{Balestriero2023ALearning}, where models learn autonomously from unlabeled data to create their own supervisory signals \cite{audioselfsupsurvey}. This method resembles how humans learn from observations and interactions, transforming unsupervised problems into supervised ones by auto-generating labels. SSL benefits include reduced dependence on labeled data, contributing to more robust and generalizable data representations.

@@

\textbf{Modulation effects}: Utilize a control signal or low-frequency oscillator. Six variables determine the \href{https://github.com/oriolcolomefont/Master-Thesis/blob/main/dataset.py}{chorus parameters}. The tremolo's amplitude modulation frequency and depth are controlled by $t_s \in [0.1, 100]$ and $t_d \in [1, 101]$, respectively.

@@

$I$ represent the set of all items in the batch, $|A_i|$, $|P_i|$, and $|N_i|$ denote the lengths of the anchor, positive, and negative vectors for the $i$-th item, respectively. The $\max$ function is applied to find the longest of these three lengths for each item, and then the maximum of these maximum lengths is taken over all items in the batch. This gives the maximum length, $L_{\text{max}}$, of any vector in the batch.

>>>>

Our implementation falls broadly under cognitive modeling, which seeks to simulate human cognitive processes and problem-solving through a computerized model. We advocate for exposure-based learning in music, encouraging active engagement with as many musical styles, genres, techniques, and learning methods as possible. This approach promotes comprehensive musical proficiency and efficient performance when encountering novel and unseen data in practical applications.

@@

Our implementation slightly modifies the CLMR method \cite{CLMR2021}, which learns valuable, discriminative music representations without explicit labels by contrasting positive augmentations of a musical piece against negative ones. CLMR falls under a branch of ML known as self-supervised learning (SSL) \cite{Balestriero2023ALearning}, where models learn autonomously from unlabeled data to create their own supervisory signals \cite{audioselfsupsurvey}. This method resembles how humans learn from observations and interactions, transforming unsupervised problems into supervised ones by auto-generating labels. SSL benefits include reduced dependence on labeled data, contributing to more robust and generalizable data representations.

@@

\textbf{Modulation effects}: Utilize a control signal or low-frequency oscillator. Six variables determine the \href{https://github.com/oriolcolomefont/Uncovering-High-Level-Content-in-the-Time-Domain/blob/24057f4160a4ecb7ccef16146ad086ab5160aef8/dataset.py#L120C9-L128C10}{chorus parameters}. The tremolo's amplitude modulation frequency and depth are controlled by $t_s \in [0.1, 100]$ and $t_d \in [1, 101]$, respectively.

@@

$I$ represents the set of all items in the batch, $|A_i|$, $|P_i|$, and $|N_i|$ denote the lengths of the anchor, positive, and negative vectors for the $i$-th item, respectively. The $\max$ function is applied to find the longest of these three lengths for each item, and then the maximum of these maximum lengths is taken over all items in the batch. This gives the maximum length, $L_{\text{max}}$, of any vector in the batch.
